A tutorial of Bayesian beta regressions with brms in R

### 2025-01-06 manuscript/manuscript.qmd
fix typo

The coefficients of a beta regression are estimated on the log-odds scale, as in Bernoulli/binomial (aka logistic) regressions. From the summary, we see that speech rate (number of syllables per second) has a positive effect on voicing proportion: the 80% CrI is between 0.01 and 0.15 log-odds \[$\beta$ = 0.8, SD = 0.06\]. Log-odds can be converted to odd-ratios by exponentiating the value: 0.01-0.15 log odds correspond to an odd-ratio of 1.01 to 1.16, or as percentages, to an increase of voicing of 1 to 16% for every increase of one syllable per second. Since this is an 80% CrI, we can be 80% confident that the true effect of speech rate is between 1-16% increase of voicing proportion, conditional on the data and model. Note that transforming measures this way is appropriate *only* with quantile-based measures (like CrIs) but not with moments like the mean and standard deviation: to correctly get mean and SDs in the transformed scale, you must first extract the posterior draws (see below), convert them and then take moments such as mean and SD (for a more detailed explanation, see XXX). In the avoidance of doubt, we will always transform the drawn values first and then take summary measures.

>>>>

The coefficients of a beta regression are estimated on the log-odds scale, as in Bernoulli/binomial (aka logistic) regressions. From the summary, we see that speech rate (number of syllables per second) has a positive effect on voicing proportion: the 80% CrI is between 0.01 and 0.15 log-odds \[$\beta$ = 0.08, SD = 0.06\]. Log-odds can be converted to odd-ratios by exponentiating the value: 0.01-0.15 log odds correspond to an odd-ratio of 1.01 to 1.16, or as percentages, to an increase of voicing of 1 to 16% for every increase of one syllable per second. Since this is an 80% CrI, we can be 80% confident that the true effect of speech rate is between 1-16% increase of voicing proportion, conditional on the data and model. Note that transforming measures this way is appropriate *only* with quantile-based measures (like CrIs) but not with moments like the mean and standard deviation: to correctly get mean and SDs in the transformed scale, you must first extract the posterior draws (see below), convert them and then take moments such as mean and SD (for a more detailed explanation, see XXX). In the avoidance of doubt, we will always transform the drawn values first and then take summary measures.

### 2025-01-06 manuscript/manuscript.tex
fix typo

The coefficients of a beta regression are estimated on the log-odds
scale, as in Bernoulli/binomial (aka logistic) regressions. From the
summary, we see that speech rate (number of syllables per second) has a
positive effect on voicing proportion: the 80\% CrI is between 0.01 and
0.15 log-odds {[}\(\beta\) = 0.8, SD = 0.06{]}. Log-odds can be
converted to odd-ratios by exponentiating the value: 0.01-0.15 log odds
correspond to an odd-ratio of 1.01 to 1.16, or as percentages, to an
increase of voicing of 1 to 16\% for every increase of one syllable per
second. Since this is an 80\% CrI, we can be 80\% confident that the
true effect of speech rate is between 1-16\% increase of voicing
proportion, conditional on the data and model. Note that transforming
measures this way is appropriate \emph{only} with quantile-based
measures (like CrIs) but not with moments like the mean and standard
deviation: to correctly get mean and SDs in the transformed scale, you
must first extract the posterior draws (see below), convert them and
then take moments such as mean and SD (for a more detailed explanation,
see XXX). In the avoidance of doubt, we will always transform the drawn
values first and then take summary measures.

>>>>

The coefficients of a beta regression are estimated on the log-odds
scale, as in Bernoulli/binomial (aka logistic) regressions. From the
summary, we see that speech rate (number of syllables per second) has a
positive effect on voicing proportion: the 80\% CrI is between 0.01 and
0.15 log-odds {[}\(\beta\) = 0.08, SD = 0.06{]}. Log-odds can be
converted to odd-ratios by exponentiating the value: 0.01-0.15 log odds
correspond to an odd-ratio of 1.01 to 1.16, or as percentages, to an
increase of voicing of 1 to 16\% for every increase of one syllable per
second. Since this is an 80\% CrI, we can be 80\% confident that the
true effect of speech rate is between 1-16\% increase of voicing
proportion, conditional on the data and model. Note that transforming
measures this way is appropriate \emph{only} with quantile-based
measures (like CrIs) but not with moments like the mean and standard
deviation: to correctly get mean and SDs in the transformed scale, you
must first extract the posterior draws (see below), convert them and
then take moments such as mean and SD (for a more detailed explanation,
see XXX). In the avoidance of doubt, we will always transform the drawn
values first and then take summary measures.
